Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex
adding bibliography

The parareal algorithm, developed by Lions, Maday and Turinici in 2001, CITE is
a generalized algorithm which allows for parallelization in time. It does so
by using a cheaper ($g_{\Delta t}$)---a lower order or lesser resolution
approximation first, which it then corrects by evaluating segments with a finer
method $g_{\textnormal{fine}}$. The correction step from the approximation can
be done in parallel. Multiple iterations can be performed to achieve an error
provably asymptotically equal to a full serial computation of
$g_{\textnormal{fine}}$. The exact number of iterations required to achieve
certain levels of convergence depends on the problem and must be tuned top
optimize for speedup for a given system. In summary, the algorithm is $k$
repetitions of a correction process which requires running updated by a finer
method run in parallel for subsections.

@@

\section{References}

@@

%\bibliographystyle{unsrt}
%\bibliography{poster/sample}

>>>>

The parareal algorithm, developed by Lions, Maday and Turinici in 2001
\cite{lions2001parareal}, is a generalized algorithm which allows for
parallelization in time. It does so by using a cheaper ($g_{\Delta t}$)---a
lower order or lesser resolution approximation first, which it then corrects by
evaluating segments with a finer method $g_{\textnormal{fine}}$. The correction
step from the approximation can be done in parallel. Multiple iterations can be
performed to achieve an error provably asymptotically equal to a full serial
computation of $g_{\textnormal{fine}}$. The exact number of iterations required
to achieve certain levels of convergence depends on the problem and must be
tuned top optimize for speedup for a given system. In summary, the algorithm is
$k$ repetitions of a correction process which requires running updated by a
finer method run in parallel for subsections.

@@

\bibliographystyle{unsrt}
\bibliography{paper}

@@
